Manuscript 1 code

### 2024-09-11 manuscript_1_code.Rmd
changed fig 1 and how join cover_long

functional_group_colours <- c("coral_mean" = "#56B4E9",
                         "cca_mean" = "#CC79A7",
                         "macroalgae_mean" = "#009E73",
                         "turf" =  "#D55E00")

@@

cover_means <- cover_df %>%
  group_by(year, habitat) %>%
  summarise(macroalgae_mean = mean(macroalgae),
            coral_mean = mean(coral),
            turf_mean = mean(turf),
            cca_mean = mean(cca),
            sand_mean = mean(sand),
            other_mean = mean(other)
            )

cover_se <- cover_df %>%
  group_by(year, habitat) %>%
  summarise(macroalgae_se = se(macroalgae),
            coral_se = se(coral),
            turf_se = se(turf),
            cca_se = se(cca),
            sand_se = se(sand),
            other_se = se(other)
            )

cover_long <- pivot_longer(
  data = cover_means,
  cols = 3:8,
  names_to = "functional_group",
  values_to = "percent_cover"
)

@@

cover_long$se <- cover_long_se$se

cover_long$habitat <- factor(cover_long$habitat, 
                             levels = c("fringing", "backreef", "outer_10","outer_17"),
                             labels = c("Fringing", "Backreef", "Forereef 10m", "Forereef 17m"))

@@

ggsave(filename = "output/figure_1.png", figure_1, height = 10, width = 14)

>>>>

functional_group_colours <- c("coral" = "darkmagenta",
                         "cca" = "pink",
                         "macroalgae" = "#004D40",
                         "turf" =  "#1E88E5")

@@

cover_means <- cover_df %>%
  group_by(year, habitat) %>%
  summarise(macroalgae = mean(macroalgae),
            coral = mean(coral),
            turf = mean(turf),
            cca = mean(cca),
            sand = mean(sand),
            other = mean(other)
            )

cover_se <- cover_df %>%
  group_by(year, habitat) %>%
  summarise(macroalgae = se(macroalgae),
            coral = se(coral),
            turf = se(turf),
            cca = se(cca),
            sand = se(sand),
            other = se(other)
            )
```

```{r cover long}
cover_long_means <- pivot_longer(
  data = cover_means,
  cols = 3:8,
  names_to = "functional_group",
  values_to = "percent_cover"
)

@@

cover_long <- left_join(cover_long_means,cover_long_se)

#make levels for habitat for plotting
cover_long$habitat <- factor(cover_long$habitat, 
                             levels = c("fringing", "backreef", "outer_10","outer_17"),
                             labels = c("Fringing", "Backreef", "Forereef 10m", "Forereef 17m"))
```

```{r simplified cover - remove}

@@

#ggsave(filename = "output/figure_1.png", figure_1, height = 10, width = 14)
